% -*- root: ../gvoysey-thesis.tex -*-
\iffalse
I begin by thanking my advisor in so many things, Dr.~H.~Steven~Colburn, who has been an example to aspire to for more than a decade.  Thank you for  your support and care.  Thank you for helping me find the questions I want to answer.   

I'd also like to thank my committee members, Dr.~Barbara~Shinn-Cunningham, Dr.~Allyn~Hubbard, and Dr.~Hideko Nakajima.  Barb, thank you for being the example by which I judge the clarity of talks, and for introducing me to the complexities of the auditory system.  Al and Heidi, thank you for your careful attention and engaging discussions.

I would not have been able to complete this work without the help of many of my colleagues and fellow researchers.  I am deeply indebted first to Dr.~Goldbarg~Mehraei, for graciously sharing her experimental data and knowledge with me.  My sincere gratitude to Dr.~Sarah~Verhulst and her group for sharing their model code with me, and Dr.~Laurel~Carney for a series of formative conversations that shaped how this project proceeded.  I'd also like to thank Gerard Encina-Llamas for being the first user of the software I developed during the course of this thesis, and for suggesting many valuable additions I wouldn't have thought of alone.

I'd like to thank all my colleagues in the Hearing Research Center.  In particular, Aleks Zosuls and Andy Brughera have been good friends and valuable resources for many years, and I'm very grateful.  I'd especially like to thank my fraa Dave Anderson, whose mentorship is the direct cause of my skills in software development and project architecture, without which this or any other computational project would've been impossible.  

I would like to thank many people in my life for their support and encouragement.   My wife, Yelena, for her tireless support, unconditional love, and  tolerance of late nights in the lab.  My son, Rory, who is yet too young to remember how helpful he's been in motivating me.  My brother, Ian, for living out the Voysey byword.  My parents, Helen and Stephen, for raising me right and instilling in me the tenacity to stay with it, and the desire to do things that make a difference.

Finally, I'd like to thank David Mountain, who saw something worthy in me. Thank you for setting the bar so high, and showing me what a life spent in an exuberant search for answers looks like. 
\fi 